Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-04-23 analyses/scripts/full_data_extraction_citation_table.Rmd
Reformated the script to remove kable settings for beautifying the tables for the database

```{r}
# Data "cleaning"
#a vector of shorter replacements for the original parametrization descriptions
parametrization_str_replacements <- c('values_from_literature' = 'literature', 
                  'values_from_guess_and_expert_opion' = 'expert_opinion', 
                  'values_fitted_to_ts' = 'fitted',
                  ' ' = ' and ' #replace space with 'and' to make it more readable
                  )

#a vector of shorter replacements for the original validation descriptions
validation_str_replacements <- c('compared_with_data' = 'data',
                                 'compared_with_other_model_output' = 'another_model',
                                 'model_not_validated' = 'none',
                                 ' ' = '_and_'
                                 )

# The data with citations 
compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')

compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>% 
    mutate(vax_modelled = ifelse(str_detect(intervention_modelled, 'vaccination'), 
                               'yes', 
                               'no')
         ) %>% 
  mutate(intervention_type = case_when(
    vax_modelled == 'no' & vax_modelled_with_non_vax == 'no' ~ 'no_vax', #Vaccination was not modelled
    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'no' ~ 'vax_combination_with_others', #when vax was modelled but not for comparison as a single intervention
    vax_modelled == 'yes' & vax_modelled_with_non_vax == 'yes' ~ 'vax_single', #when vax was modelled as a single intervention
  )) %>% 
  mutate(publication_year = as.numeric(publication_year), 
         author_in_country_studied = as.character(author_in_country_studied)) %>% 
  arrange(publication_year) %>%
  mutate(
    author_affiliation_type = str_replace_all(author_affiliation_type, ' ', ' + '),
    author_in_country_studied = if_else(author_in_country_studied == 'NA', 'not_applicable',
                                        author_in_country_studied
                                        )
    ) %>% 
  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, #An approach to aggregate the years before 2006 into one group because of the low number of papers
                                         2005, 
                                         publication_year
                                         )
                                  ), 
         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'purely_academic', 
                                         'mixed')
                                 )
         )

#replace the original descriptions of parametrization and validation with shorter strings
compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
  mutate(parametrization = str_replace_all(parametrization, 
                                           parametrization_str_replacements
                                           )
         ) %>% 
  mutate(validation = str_replace_all(validation, 
                                      validation_str_replacements
                                      )
         ) %>% 
  mutate(model_structure = str_replace(model_structure, 'deterministic stochastic', 'both'))

#Rearrange the columns
compact_data_with_citation_keys <- compact_data_with_citation_keys %>% 
  relocate(c(title, bibtexkey), .before = publication_year) %>% 
  relocate(publication_year, .before = bibtexkey) %>% 
  relocate(c(x0_reviewer, category, author:language), 
           .after = collab_type
           )
```

```{r results='asis'}
final_citation_table <- compact_data_with_citation_keys %>% 
    relocate(c('doi', 'year', 'bibtexkey'), .after = title) %>% 
    select(-c(year_aggreg, x0_reviewer, category, 
              number, pages, journal, publisher, 
              volume, language, month, publication_type, 
              modelling_timing, intervention_type, collab_type,
              author, paper_doi, year, 
              doi, bibtexkey
              )
           ) %>% 
    arrange(desc(publication_year))
```

```{r}
#columns 2-5 with paper titles
kable(final_citation_table %>% 
                 dplyr::select(1:5), 
             format = "latex", 
             booktabs = TRUE, 
             longtable = FALSE#,
             #caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    column_spec(column = c(1, 3), width = "5cm") %>%
    landscape()
```

```{r}
#columns 6-10 with paper titles
kable(final_citation_table %>% 
                 dplyr::select(1, 6:10), 
             format = "latex", booktabs = TRUE, 
             longtable = FALSE#,
             #caption = 'Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    column_spec(column = c(1), width = "5cm") %>% 
    landscape()
```

```{r}
#columns 11-15 with paper titles
kable(final_citation_table %>% 
                 dplyr::select(1, 11:15), 
             format = "latex", booktabs = TRUE, 
             longtable = FALSE#,
           #  caption = 'Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    column_spec(column = c(1, 2, 5), width = "4cm") %>% 
    landscape()
```

```{r}
#columns 16-22 with paper titles
kable(final_citation_table %>% 
                 dplyr::select(1, 16:22), 
             format = "latex", booktabs = TRUE, 
             longtable = FALSE#,
           #  caption = 'Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled.'
             ) %>% 
    kable_styling(latex_options = c('striped', 'scale_down', 'hold_position', 'repeat_header')) %>% 
    column_spec(column = c(1, 3), width = "5cm") %>% 
    landscape()
```

>>>>

```{r}
# Load the data with citations
compact_data_with_citation_keys_init <- read_rds("../data/compact_data_with_citation_keys_cleaned.rds")

# Clean various variables
compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>%
  mutate(vax_modelled = ifelse(str_detect(intervention_modelled, "vaccination"),
    "yes",
    "no"
  ), 
  intervention_type = case_when(
    vax_modelled == "no" & vax_modelled_with_non_vax == "no" ~ "no_vax", # Vaccination was not modelled
    vax_modelled == "yes" & vax_modelled_with_non_vax == "no" ~ "vax_combination_with_others", # when vax was modelled but not for comparison as a single intervention
    vax_modelled == "yes" & vax_modelled_with_non_vax == "yes" ~ "vax_single", # when vax was modelled as a single intervention
  ),
    publication_year = as.numeric(publication_year),
    author_in_country_studied = as.character(author_in_country_studied)
  ) %>%
  arrange(publication_year) %>%
  mutate(
    author_affiliation_type = str_replace_all(author_affiliation_type, " ", " + "),
    author_in_country_studied = if_else(author_in_country_studied == "NA", "not_applicable",
      author_in_country_studied
    ),
    year_aggreg = as.numeric(ifelse(publication_year < 2006, # An approach to aggregate the years before 2006 into one group because of the low number of papers
      2005,
      publication_year
    )),
    collab_type = as_factor(if_else(author_affiliation_type == "academic_institutions",
      "purely_academic",
      "mixed"
    ))
  )
```

```{r}
# Data dictionaries

# parametrization description dictionary
parametrization_str_replacements <- c(
  "values_from_literature" = "literature",
  "values_from_guess_and_expert_opion" = "expert_opinion",
  "values_fitted_to_ts" = "fitted",
  " " = " and " # replace space with 'and' to make it more readable
)

# validation description dictionary
validation_str_replacements <- c(
  "compared_with_data" = "data",
  "compared_with_other_model_output" = "another_model",
  "model_not_validated" = "none",
  " " = "_and_"
)

# Clean the parametrization and validation variables with dictionary
compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
  mutate(parametrization = str_replace_all(
    parametrization,
    parametrization_str_replacements
  )) %>%
  mutate(validation = str_replace_all(
    validation,
    validation_str_replacements
  )) %>%
  mutate(model_structure = str_replace(model_structure, 
                                       "deterministic stochastic", 
                                       "both"
                                       )
         )
```

```{r}
# Rearrange the columns
compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
  relocate(c(title, bibtexkey), .before = publication_year) %>%
  relocate(publication_year, .before = bibtexkey) %>%
  relocate(c(x0_reviewer, category, author:language),
    .after = collab_type
  )
```

```{r}
# Remove unneeded columns and rearrange the remainder
 final_citation_table <- compact_data_with_citation_keys %>% 
     relocate(c('doi', 'year', 'bibtexkey'), .after = title) %>% 
     select(-c(year_aggreg, x0_reviewer, category, 
               number, pages, journal, publisher, 
               volume, language, month, publication_type, 
               modelling_timing, intervention_type, collab_type,
               author, paper_doi, year, 
               doi, bibtexkey
               )
            ) %>% 
     arrange(desc(publication_year))
```

```{r}
# Make a neat table of papers from columns 1(title)-5
final_citation_table %>% 
    select(1:5) %>% 
    kable()

# booktabs = TRUE,
#       longtable = FALSE#,
#       # caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
#          ) %>%
#     kable_styling(latex_options = c('striped',
#                                     'scale_down',
#                                     'hold_position',
#                                     'repeat_header'
#                                     )
#                   ) %>%
#     column_spec(column = c(1, 3), width = "5cm") #%>%
    # landscape()
```

<!--  ```{r} -->
<!-- # Make a neat table of papers from columns 1 (title), and 6-10  -->
<!-- final_citation_table %>% -->
<!--   select(c(1, 6:10)) %>% -->
<!--   kable( -->
<!--     booktabs = TRUE, -->
<!--     longtable = FALSE, -->
<!--     caption = "Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure." -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("striped",  -->
<!--                                   "scale_down",  -->
<!--                                   "hold_position",  -->
<!--                                   "repeat_header" -->
<!--                                   ) -->
<!--                 ) %>% -->
<!--   column_spec(column = c(1), width = "5cm") %>% -->
<!--   landscape() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Make a neat table of papers from columns 1 (title) and 11-15  -->
<!-- final_citation_table %>% -->
<!--   select(1, 11:15) %>% -->
<!--   kable( -->
<!--     longtable = FALSE, -->
<!--     caption = "Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax." -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("striped",  -->
<!--                                   "scale_down",  -->
<!--                                   "hold_position",  -->
<!--                                   "repeat_header" -->
<!--                                   ) -->
<!--                 ) %>% -->
<!--   column_spec(column = c(1, 2, 5), width = "4cm") %>% -->
<!--   landscape() -->
<!-- ``` -->

<!--  ```{r} -->
<!-- # Make a neat table of papers from columns 1 (title) and 16-22 -->
<!-- final_citation_table %>% -->
<!--   select(1, 16:22) %>% -->
<!--   kable( -->
<!--     booktabs = TRUE, -->
<!--     longtable = FALSE, -->
<!--     caption = "Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled." -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("striped", -->
<!--                                   "scale_down",  -->
<!--                                   "hold_position",  -->
<!--                                   "repeat_header" -->
<!--                                   ) -->
<!--                 ) %>% -->
<!--   column_spec(column = c(1, 3), width = "5cm") %>% -->
<!--   landscape() -->
<!-- ``` -->
